---
title: 'Inference Project4: Simulation Exercise'
author: "Shuai Wang"
date: "Dec, 11, 2016"
output:
  html_document: default
  pdf_document: default
fig_caption: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,cache=F,message=F, warning=F)
```
## Part 1: Simulation Exercise

#### Title: 

Comparing Simulation Results of exponential distribution with Central Limit Theorem  

#### Overview: 

In the first part of the project, I will run simulation results of exponential distribution. The exponential distribution number generator is based on rexp() function.

#### Simulations:

```{r}
# setting up the experiment parameters
nosim <- 1000
n <- 40
lambda <- 0.2
simulated<-matrix(rexp(nosim * n, lambda), nosim)
plot(hist(simulated),xlab="Value",ylab="Frequency",col="blue",main="Histogram Plot of 1000 Exponential Distribution Simulation Runs")
```

From the instruction, we know that the the mean of exponential distribution is 1/lambda and the standard deviation is also 1/lambda.

#### Sample Mean versus Theoretical Mean: 
_Include figures with titles. In the figures, highlight the means you are comparing. Include text that explains the figures and what is shown on them, and provides appropriate numbers._

Here in the figure below. I present the distribution of the normalized means of 1000 simulations in blue histogram plot. I also plot standard normal distribution in the black curve.
```{r}
#plot(hist_plot,xlab="Value",ylab="Frequency",col="blue",main="Histogram Plot of One Exponential Distribution Simulation Run")
observed.mean<-apply(simulated, 1, mean)
normalizedMean<-observed.mean-1/lambda
normalizedData<-normalizedMean*sqrt(40)/(1/(lambda))
hist(normalizedData,xlab="",ylab="",yaxt='n',xaxt='n',main="",col="blue")
par(new=TRUE)
x<-rnorm(1000, mean = 0, sd = 1)
p<-density(x,main="",xlab="",ylab="")
plot(p,main="",xlab="",ylab="")
title(main="Distribution of Means of Exponential with Normal Distribution Overlap",xlab="value",ylab="Frequency",sub="Figure 1. Simulated Exercise")
#observed.sd
observed.var<-var(apply(simulated,1,mean))
#observed.var
#sqrt(observed.var)
#abline( v = observed.mean, col = "black")
#text(1,0, "Obsevered Mean", col = "white", adj = c(0, -.1))
#abline( v = 1/lambda, col = "red")
#text(3,0, "Theoretical Mean", col = "white", adj = c(0, -.1))
```

#### Sample Variance versus Theoretical Variance:

_Include figures (output from R) with titles. Highlight the variances you are comparing. Include text that explains your understanding of the differences of the variances._
```{r}
observed.var<-var(observed.mean)
sprintf("The observed variance of mean should be:%.2f",observed.var)
expected.var<-(1/lambda^2)/n
sprintf("The expected variance of mean should be:%.2f",expected.var)
```

#### Distribution: 

_Via figures and text, explain how one can tell the distribution is approximately normal._

Based on the Central Limit Theorem, we learn that the mean of random distributions follow standard normal distribution when the repetition of simiulations gets larger. From figrue 1, we can see that the distribution of 1000 means of 40 expeontials follow nicely with the standard normal distribution. The observed variance of the mean is also about the same as the expected variance of the mean. From these results, we can tell the distribution is approximately normal.

