---
title: "InferenceProject4"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,cache=T)
```
## Part 1: Simulation Exercise

### Title: Comparing Simulation Results of exponential distribution with Central Limit Theorem  

### Overview: In the first part of the project, I will run simulation results of exponential distribution. The exponential distribution number generator is based on rexp() function.

### Simulations:
```{r}
# setting up the experiment parameters
nosim <- 1000
n <- 40
lambda <- 0.2

```
From the instruction, we know that the the mean of exponential distribution is 1/lambda and the standard deviation is also 1/lambda
### Sample Mean versus Theoretical Mean: Include figures with titles. In the figures, highlight the means you are comparing. Include text that explains the figures and what is shown on them, and provides appropriate numbers.

### Sample Variance versus Theoretical Variance: Include figures (output from R) with titles. Highlight the variances you are comparing. Include text that explains your understanding of the differences of the variances.

### Distribution: Via figures and text, explain how one can tell the distribution is approximately normal.

## Part 2: Basic Inferential Data Analysis

### load the ToothGrowth data and perform some basic exploratory data analyses
```{r}
library(datasets)
data(ToothGrowth)
library(ggplot2)
library(reshape2)
ToothGrowth$supp<-as.factor(ToothGrowth$supp)
ToothGrowth$dose<-as.factor(ToothGrowth$dose)
melted_data<-melt(ToothGrowth,id.vars=c("supp","dose"))
#some ggplot examples are from http://www.cookbook-r.com/Graphs/Plotting_means_and_error_bars_(ggplot2)/

library(Rmisc)#get the mean, sd information for plotting
melted_data.Summary<-summarySE(melted_data, measurevar="value", groupvars=c("supp","dose"))
ggplot(melted_data.Summary, aes(x=dose, y=value, fill=supp)) +
  geom_bar(position=position_dodge(), stat="identity") +
  geom_errorbar(aes(ymin=value-se, ymax=value+se),
              width=.2,               # Width of the error bars
              position=position_dodge(.9))


  # Use 95% confidence intervals instead of SEM

    ggplot(melted_data.Summary, aes(x=dose, y=value, fill=supp)) + 
    geom_bar(position=position_dodge(), stat="identity") +
    geom_errorbar(aes(ymin=value-ci, ymax=value+ci),
              width=.2,                    # Width of the error bars
              position=position_dodge(.9))
```
### Provide a basic summary of the data.
```{r}
summary(ToothGrowth)
```
### Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose. (Only use the techniques from class, even if there's other approaches worth considering)

### State your conclusions and the assumptions needed for your conclusions.
```{r pressure, echo=FALSE}
plot(pressure)
```
